Approximation as Differentiation notes

### 2025-03-03 notes/sec/grothendieck.tex
New notation better.

\begin{enumerate}
\item $[X, Y]$ to be the object $(\Fam(C)(X,Y),[X, Y])$ in $\Fam(C)$ where we also write $[X,Y]$ for the
indexed family which maps every $(f: I \to J, g: X \to \reindex{Y}{f}): X \to Y$ in $\Fam(C)$ to
$\prod_{I}\reindex{Y}{f}$.
\item The family of isomorphisms $\lambda_{X,Y,Z}$ (natural in $X$) which sends any morphism $f: X \times Y
\to Z$ to the morphism $g: X \to [Y, Z]$ with:
\begin{itemize}
\item $\idxf{g}(i) = (j \mapsto \idxf{f}(i, j): J \to K, j \mapsto \famf{f}_{i,j} \comp \inj_{Y_j}: Y \to
\reindex{Z}{j \mapsto \idxf{f}(i, j)})$ where $\inj_{Y_j}: Y_j \to X_i \biprod Y_j$
\item $\famf{g}(i) = \lambda_{\prod_{J}}(j \mapsto \famf{f}_{i, j} \comp \inj_{X_i})$ where $\inj_{X_i}: X_i
\to X_i \biprod Y_j$ for every $j \in J$
\end{itemize}
\item The family of morphisms $\eval_{X,Y}: [X, Y] \times X \to Y$ in $\Fam(C)$ with
\begin{itemize}
\item $\idxf{\eval}_{X,Y}((f, g), i) = f(i)$
\item $\famf{\eval}_{X,Y}((f, g), i) = \coprodM{{\eval_{\prod}}_i}{g_i}: \prod_{I}\reindex{Y}{f} \biprod X_i \to Y_{f(i)}$
\end{itemize}
using $\coprodM{-}{-}$ to denote coproduct of morphisms.
\end{enumerate}
Then for any $f: X \times Y \to Z$ in $\Fam(C)$ we have \todo{(prove these)}:
\begin{enumerate}
\item The following diagram commutes:

>>>>

\begin{enumerate}
\item $[X, Y]$ to be the object $(\Fam(C)(X,Y),[\idxf{X}, \idxf{Y}])$ in $\Fam(C)$ where $[\idxf{X},
\idxf{Y}]$ denotes the indexed family which maps every $f: X \to Y$ in $\Fam(C)$ to
$\prod_{I}\reindex{Y}{\idxf{f}}$.
\item The family of isomorphisms $\lambda_{X,Y,Z}$ (natural in $X$) sending any morphism $f: X \times Y \to Z$
to $g: X \to [Y, Z]$ with:
\begin{itemize}
\item $\idxf{g}(i) = (j \mapsto \idxf{f}(i, j): J \to K, j \mapsto \famf{f}_{i,j} \comp \inj_{Y_j}: Y \to
\reindex{Z}{j \mapsto \idxf{f}(i, j)})$ where $\inj_{Y_j}: Y_j \to X_i \biprod Y_j$
\item $\famf{g}(i) = \lambda_{\prod_{J}}(j \mapsto \famf{f}_{i, j} \comp \inj_{X_i})$ where $\inj_{X_i}: X_i
\to X_i \biprod Y_j$ for every $j \in J$
\end{itemize}
\item The family of morphisms $\eval_{X,Y}: [X, Y] \times X \to Y$ in $\Fam(C)$ with
\begin{itemize}
\item $\idxf{\eval}_{X,Y}((f, g), i) = f(i)$
\item $\famf{\eval}_{X,Y}((f, g), i) = \coprodM{{\eval_{\prod}}_i}{g_i}: \prod_{I}\reindex{Y}{f} \biprod X_i \to Y_{f(i)}$
\end{itemize}
using $\coprodM{-}{-}$ to denote coproduct of morphisms.
\end{enumerate}
Then for any $f: X \times Y \to Z$ in $\Fam(C)$ we have \todo{(prove these)}:
\begin{enumerate}
\item The following diagram commutes:
